`SimSurvey`: an `R` package for comparing the design and analysis of fisheries surveys by simulating spatially-correlated fish stocks

### 2019-12-19 analysis/paper/rebuttal_letter.Rmd

The manuscript might be easier to follow if the manuscript was restructured: 1) Model description, 2) Using SimSurvey. The later section would then group all example code which could again be subdivided into running simulations and exploring results (plot functions).

*This is an excellent suggestion! We have re-structured our manuscript accordingly and feel that this structure will be much easier for a reader to follow.*

3. Parameterisation
To use SimSurvey for a real world problem realistic parameter values are needed. The package comes with default values chosen for a particular case study. However, no mention is made in the manuscript how to choose appropriate values for the many model parameters to tailor the simulations to a population of interest. I suggest the authors add a section on parameterisation and a table summarizing all parameters with a column specifying how to parameterize. For example, parameters for population dynamics and growth could probably be taken from the literature (or a stock assessment report). However this is not possible for the parameters of the spatial distribution function sim_distribution() such as correlation between ages etc. Ideally the package would include a fitting function for estimating these parameters from actual data. These input data could come from a pilot survey and include location (lat, long) and numbers by length/age.

*This is yet another very helpful suggestion and, now that we have included a Parameterisation section, it is easy to see the value of such a section to prospective users of the package. However, we should note that we deviated from the recommendation to a degree as we did not produce a table that summaries how to specify the parameters, rather we wrote a section that outlines recommended steps for setting up a custom simulation. We started drafting a table, however, it quickly became apparent that it would be too big and cumbersome and somewhat redundant with the core tables that describe the arguments and parameters. We hope that the narrative/outline we included will serve the practical purpose the reviewer had in mind.*

### 2019-12-19 analysis/paper/sim_survey_paper.Rmd
Draft Parameterisation section (suggested by reviewer 2)

cat("1. Adjust font size of code strings (title and headers, and convert links to sections with code to code font [Using SimSurvey and test_surveys])  \n")
cat("2. Decrease font size of tables  \n")
cat("3. Indent closures in Table \\@ref(tab:fun)  \n")
cat("4. Replace pluses (`+`) with spaces in Tables \\@ref(tab:abundance) to \\@ref(tab:survey)  \n")
cat("5. Adjust size of footnote below Table \\@ref(tab:abundance)  \n")
cat("6. Adjust size of Figure \\@ref(fig:real-sim-comp)  \n")
cat("7. Place supplements in separate documents  \n")
cat("8. Remove this section  \n")

@@

>>>>

cat("1. Adjust font size of code strings (title and headers, and convert links to sections with code to code font [Using SimSurvey, test_surveys])  \n")
cat("2. Decrease font size of tables  \n")
cat("3. Indent closures in Table \\@ref(tab:fun)  \n")
cat("4. Replace pluses (`+`) with spaces in Tables \\@ref(tab:abundance) to \\@ref(tab:survey)  \n")
cat("5. Adjust size of footnote below Table \\@ref(tab:abundance)  \n")
cat("6. Adjust size of Figure \\@ref(fig:real-sim-comp)  \n")
cat("7. Place supplements in separate documents  \n")
cat("8. Remove this section  \n")

@@

# Parameterisation

The default parameter values used in this package were chosen to emulate  survey data from a specific cod population (see **[S1 Appendix][S1 Appendix: Case study]** for details) and, as such, these values ought to provide a good place to start for another population of cod. In this section we outline a series of recommended steps to take to tailor the default settings to suit another system. Throughout this outline, we also provide some context on how default parameter values were chosen as this information may help guide a users' choices.

## 1. Define survey area and protocol

Parameterising the survey design should be the easiest place to start as the area and protocol should be clearly defined. The survey area can be defined using `make_grid` or it can be manually constructed. For the case study, `make_grid` arguments were modified to create a grid with similar dimensions to the stratified design actually applied to the case study area (i.e. total area, shelf depth, number of strata, etc.). Also note that the resolution (`res` argument) of the grid was defined to be similar to the resolution at which sets are allocated in the survey. A square grid was chosen in lieu of the actual survey grid to create an area that avoids potential issues associated with land as a barrier while being sufficiently complex to test survey designs. When setting up a grid, be careful not to drastically increase the dimensions (`x_range` or `y_range` arguments) or resolution (`res` argument) as simulating the spatial noise over a large field can be computationally demanding.

With a survey grid defined, the settings of `sim_survey` can be modified to match the protocol of a users' survey of interest. For the case study, the trawl dimensions (`trawl_dim`) were modified to match the dimensions of a standard trawl conducted in the region. Likewise, area is used to define the number of sets to allocate to a strata and the value used by default for `set_den` matches the protocol, as does the `min_sets` setting (i.e. at least two sets are conducted in each strata to facilitate stratified analyses). Finally, length and age sub-sampling settings were modified to match the protocol for the survey of cod in the case study area. The most difficult parameter to define in the `sim_survey` function is `q`. A logistic curve is used by default to define these unknown values and the `sim_logistic` parameters were tweaked to approximate the catchability curve supplied to the survey-based model that was used to assess the case study population [@ings2019]. A similar tactic can be applied to other cases with estimates of survey catchability.

## 2. Define abundance and growth parameters

Abundance and growth parameters are more difficult to define than the survey protocol as the true values are unknown. Nevertheless, spatially-aggregated age-structured models are frequently applied to assess fish populations and estimates from such models can be used to define `sim_abundance` argument settings. Alternatively, key values from these models (e.g. Z and N matrices) can be used instead of simulated values. Default parameters used in `sim_abundance` were largely inspired by estimates from the survey-based model used to assess the stock [@ings2019]. Based on this work, average total mortality was roughly centered around 0.5 ($\mu_Z$; argument `log_mean` in `sim_Z` closure) and we allowed it to make similar changes in magnitude through time and across ages by setting the standard deviation of log total mortality to 0.2 ($\sigma_Z$; argument `log_sd` in `sim_Z` closure) and the correlations to 0.9 and 0.5 in the age and year dimensions ($\varphi_{\delta, \mathrm{age}}$ and $\varphi_{\delta, \mathrm{year}}$; `phi_age` and `phi_year`), respectively. Likewise, `sim_R` values were modified to generate similar patterns in recruitment as those estimated by the model. Ages groups to simulate across ranged from age 1 to 20 ($a$; `ages` argument) to capture the tails of the population, and 20 years were simulated ($y$; `years` argument) to capture some dynamics. Finally, von Bertalanffy growth parameters were roughly based on estimates from cod in the region [@Cadigan2016b]. While the choices made are obviously imperfect and ad hoc, it is not necessary to generate a perfect representation of the population as the goal here is to generate a dynamic population to survey. What is key is that we work with a known population from which we can evaluate the performance of specific survey designs and analyses.

## 3. Define spatial parameters

Ideally this step would be no more difficult than step 2 as the inputs required could come from a spatially-explicit age-structured model fit to real data. Such estimates, however, are rare and we can confirm that no such model has been developed and fit to data from our case study population. Unless a user has access to such estimates, parameter estimates will need to manually defined using visual comparisons of real and simulated data. A user will have a first-cut simulation of some survey data by following steps 1 and 2, and the plotting functions provided with the package will provide a means of visually exploring these data. For comparison purposes, actual survey data will need to be processed and visual patterns in the spatial distribution of each age will need to be inspected. It was in this step that we noticed that ages 1 to 4 tend to occupy different areas while ages 5+ occupy similar space for the cod population we focused on. This observation motivated the coupling of the spatial noise of ages 5+ (`group_ages` argument in the `sim_ays_covar` closure), which forces this component of the population to occupy the same space, and the moderate value of 0.5 for the correlation in the spatial distribution across ages ($\varphi_{\xi, \mathrm{age}}$; `phi_age` argument in the `sim_ays_covar` closure). Year-to-year plots of the real data also revealed considerable inertia in the space occupied by each age group; this observation motivated a fairly high value of 0.9 for the correlation in the spatial distribution across years ($\varphi_{\xi, \mathrm{year}}$; `phi_year` argument in the `sim_ays_covar` closure). Finally, the range of the spatial correlation ($r$; `range` argument in the `sim_ays_covar` closure) was iteratively modified until the simulated population exhibited a similar level of patchiness as the real data, and the standard deviation of the age-year-space process ($\sigma_{\xi}$; `sd` argument in the `sim_ays_covar` closure) was increased to generate set catches with tails similar to those observed in the real data (cod catches in the area tend to be zero-inflated and heavy-tailed). Finally, visual inspection of the real data revealed that the largest catches tended to be centered on sets conducted in 200 m of water; a parabolic relationship, defined using the `sim_parabola` closure, with a mean of 200 m and standard deviation of 70 m approximated this pattern.
